# Labtools

Lab tools is a R package currently under development to aid in the creation and maintenance of research notebooks. 
By leveraging the functionality of `knitr`, `git`, and the Bootstrap web framework, this package allows for efficient creation of HTML lab notebooks from notes in Rmd files. 
This facilitates reproducible, version controlled, easily shared research notes/analyses on all major operating systems using free, open source software. 

Currently, the primary focuses are:

* Functions to create a standardized rmarkdown notebook template that can be "built" into a website simply by following a specified folder structure and naming convention (inspired by [Noble 2009](http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1000424#pcbi-1000424-g001)).
* Functions to create rmarkdown "recipes" for typical molecular biology laboratory techniques (e.g. PCR and dilutions). 
* Functions to parse the file formats returned by laboratory equipment (e.g. nanodrop and qubit, etc)

## Installation

Labtools is an R package available on GitHub, so it can installed from the RStudio console or an R command line session using the `devtools` command `install_github`.
First, make sure `devtools` is installed:

```{r, eval=FALSE}
install.packages("devtools")
```

Next, install the package from GitHub by entering:

```{r, eval=FALSE}
devtools::install_github("grunwaldlab/labtools")
```

The package should now be installed and can be loaded using:

```{r, eval=FALSE}
library(labtools)
```

