---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The primary puropse of this package is to provide a way to combine `.html` files scattered throughout a file system into a single website with a hierarchical dropdown menu.
The locations html files are displayed on the website and the hierarchy of the menu itself is determined by the names of the files/directories in html files' path or customized using configuration files.

Lets start by making a simple website from the vignettes you are reading right now. 
You can find the location of installed package files using the `system.file` command included with R:

```{r}
vignette_path <- system.file("doc", package = "quiltr")
print(vignette_path)
```

This directory contains the vignette HTML files for `quiltr` along with other asociated files: 

```{r}
list.files(vignette_path)
```

We will use this directory as the source of the information to build the website. 
We can also specify a directory to make the output in. 

```{r, eval=FALSE}
library(quiltr)
make_website(path = vignette_path, output = "./first")
```

```{r, eval=FALSE, echo=FALSE}
out <- "~/repositories/quiltr/inst/doc/first"
dir.create(out)
make_website(path = vignette_path, output = out, overwrite = TRUE)
```


We can see the result below:

<iframe src="`r system.file("doc", "first", "website", "index.html", package = "quiltr")`" width = "100%", height = "500px">



```{r, eval=FALSE}
make_website(path = vignette_path, output = "./second", use_file_suffix = TRUE)
```

```{r, eval=FALSE, echo=FALSE}
out <- "~/repositories/quiltr/inst/doc/second"
dir.create(out)
make_website(path = vignette_path, output = out, overwrite = TRUE, use_file_suffix = TRUE)
```

