---
title: The `quiltr` Package
output: 
  rmarkdown::html_vignette:
    toc: false
    css: custom.css
vignette: >
  %\VignetteIndexEntry{Package introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

Currently, the primary focus of the package is automated website creation by combining HTML files scattered throughout a directory structure.
The hierarchical menu of the website can be derived from HTML file names/paths or custom configuration files. 
This is done without imposing/assuming any particular directory structure or HTML syntax, making it extremely flexible and easy to use. 

## Installation

quiltr is an R package available on GitHub, so it can be installed from the RStudio console or an R command line session using the `devtools` command `install_github`.
First, make sure `devtools` is installed:

```{r, eval=FALSE}
install.packages("devtools")
```

Next, install the package from GitHub by entering:

```{r, eval=FALSE}
devtools::install_github("grunwaldlab/quiltr")
```

The package should now be installed and can be loaded using:

```{r, eval=FALSE}
library(quiltr)
```
