---
title: "Readme first"
output: html_document
---

## Introduction

This directory is a Quiltr template. 
It is meant to provide a starting point for Quiltr projects and demonstrate functionality for beginners.
A template like this is not needed to use `quilt`.


## Making this directory into a website

To make this directory into a website, execute `quilt` with the `path` option set to this directory.
For example, if this directory is named "default" and located in "/path/to/template", then the following R command entered into an R console would make a website from this directory. 

```{r, eval=FALSE}
quilt(path = "/path/to/template/default")
```

If no path is given to the `quilt` function, then it is assumed to be the current working directory. 
Use `getwd()` to see your current working directory and `setwd("/path/to/template/default")` to change your current working directory to "/path/to/template/default".
For example, the following code has the same effect as the first example.

```{r, eval=FALSE}
setwd("/path/to/template/default")
quilt()
```


## What each file does

### The *.Rmd files 

These files (including this one you are reading) are used to make the content of the website.
They are meant to serve as examples and to be replaced by your own content.
Unlike most other files types, which are simply displayed, `Rmd` and `md` files are [knitted](http://yihui.name/knitr/) and the result is displayed.

### quilt_config.yml

These files contain a list in YAML format that overrides default options for the `quilt` function.
The `quilt` function will look for a files named "quilt_config.yml" (specified by the `config_name` option) in the target directory and use it to set option defaults.
Configuration files will be used anywhere in the target directory hierarchy (i.e. including sub-directories) and config file further down the directory hierarchy (i.e. sub-directories) will override the settings of config files in parent directories. 
When a target directory is not specified (e.g. `quilt()`), it is assumed to be the current working directory.
This file allows the website to be built by simply running `quilt()` each time, without the need to remember the which options to use.
Using configuration files is not necessary, but is recommended; there are some things that can be done with nested configuration files that cannot be done otherwise. 

### Other files

Other files in this directory are here to demonstrate some of the file types that can be used by `quilt` and how they appear on the website.
They are meant to serve as examples and to be replaced by your own content; they are not necessary.
